### 2021-02-18 architecture.tex
Remove an obsolete todo
Minor rewording: the > a
Add an intro paragraph for Architecture (WIP)

This section describes a structure of a symbol precedence recommender.
When presented with a \gls{cnf} problem $P = (\Sigma, \mathit{Cl})$,
the recommender generates a precedence $\pi^*$ of symbols $\Sigma$.

@@

% TODO: Experiments: Increase depth and message size

>>>>

This section describes the structure of a symbol precedence recommender.
When presented with a \gls{cnf} problem $P = (\Sigma, \mathit{Cl})$,
the recommender generates a precedence $\pi^*$ of symbols $\Sigma$.

\subsection{System overview}

The precedence recommender is a system that takes
a \gls{cnf} problem $P = (\Sigma, \mathit{Cl})$ as the input,
and produces a precedence of the symbols $\Sigma$ as the output.

The input problem is assumed to be specified in the \gls{cnf} fragment
of the \acrshort{tptp} language.
% http://www.tptp.org/TPTP/SyntaxBNF.html
Note that if the input problem is specified in \gls{fof},
it can be converted to \gls{cnf} by an \gls{atp} such as Vampire.

@@
